\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}
\renewcommand{\arraystretch}{1.18}

\begin{document}

\begin{center}
{\Large \textbf{Code and Data Access Statement for Peer Review}}\\[0.5em]
{\large Manuscript: A Kolmogorov--Arnold Network-Based Learning Framework for Fractional-Order Viscoelastic Constitutive Models}\\[0.4em]
Prepared for submission to \emph{Mathematics and Computers in Simulation}\\
Date: June 10, 2026
\end{center}

\section*{Repository}

The source code and reviewer-facing reproducibility materials for this manuscript are provided at:

\begin{center}
\url{https://github.com/XIAOYANGSREN/MATCOMRevise}
\end{center}

The repository is intended to support peer review of the revised manuscript. It contains the executable source code, environment files, reproduction instructions, and lightweight tabular outputs. The full raw experimental data files and binary run artifacts are also provided in the supplementary archive submitted with the manuscript. Upon acceptance, the final reviewed code/data snapshot will be preserved in a long-term repository such as Zenodo, Figshare, or Mendeley Data, and a permanent DOI will be added to the article's Data Availability statement.

\section*{Contents}

The repository and accompanying reproducibility package are organized as follows:

\begin{tabular}{>{\ttfamily}p{0.30\linewidth}p{0.62\linewidth}}
README.md & Overview, environment notes, and reproduction commands.\\
03\_code/ & Core code for the three main manuscript examples and figure-generation scripts.\\
04\_new\_experiments/ & Revision experiments, including convergence, robustness, sensitivity, timing, real-data fitting, Prony mismatch, creep, and arbitrary-loading tests.\\
results\_paper/ & Submitted representative outputs for the three main examples. Lightweight text outputs are mirrored in the repository; full binary artifacts are kept in the supplementary archive and final DOI archive.\\
data/ & Experimental relaxation and creep data used in the real-data validation. Large raw spreadsheet files are included in the supplementary archive and final DOI archive.\\
pykan/ & Vendored copy of the pykan implementation used by the experiments, with its own license.\\
FIGURE\_MANIFEST.md & Mapping between manuscript figures and the scripts/results that generate them.\\
requirements.txt & Python package versions used for the submitted runs.\\
\end{tabular}

\section*{Environment}

The submitted runs used Python 3.12 with PyTorch 2.7.1+cu118, NumPy, SciPy, Matplotlib, Pandas, and related scientific Python packages. The complete pinned environment is given in \texttt{requirements.txt}. A CUDA-capable GPU accelerates training, but the verification scripts and many post-processing scripts can also run on CPU.

\section*{Basic Reproduction Commands}

\begin{verbatim}
git clone https://github.com/XIAOYANGSREN/MATCOMRevise.git
cd MATCOMRevise
python -m venv .venv
# Activate the virtual environment, then install dependencies:
pip install -r requirements.txt

cd 03_code
python src/verify_math.py
python src/run_all_examples.py
\end{verbatim}

For individual main examples:

\begin{verbatim}
python src/run_all_examples.py --example 1
python src/run_all_examples.py --example 2
python src/run_all_examples.py --example 3
\end{verbatim}

The revision experiments are stored in \texttt{04\_new\_experiments/}. Each experiment writes its outputs to its local \texttt{results/} directory. The figure-to-script mapping is listed in \texttt{FIGURE\_MANIFEST.md}.

\section*{Notes for Reviewers}

\begin{itemize}[leftmargin=*]
\item The repository is provided to make the numerical examples, revision experiments, and figure-generation workflow inspectable during peer review.
\item The repository mirrors the executable code and lightweight outputs. The full journal supplementary archive contains the large raw spreadsheets and binary artifacts needed for exact no-retraining regeneration of every submitted figure.
\item Some full training runs may take substantial time, especially on CPU, because the fractional-history residuals scale quadratically with the number of time points.
\item The final archival release after acceptance will include the reviewed code/data snapshot and will be assigned a permanent DOI.
\end{itemize}

\section*{Suggested Data Availability Wording}

The source code and scripts required to reproduce the numerical results are available at \url{https://github.com/XIAOYANGSREN/MATCOMRevise}. The full review package, including large raw data files and binary run artifacts, is provided with the manuscript. The final accepted version will be archived in a permanent repository with a DOI.

\end{document}
